---
title: "Project"
author: "Team 1"
date: "2022-10-27"
output: pdf_document
---
#### Load the data
```{r}
df<-read.csv('googleplaystore.csv')
#View(df)
```

```{r}
colSums((is.na(df)) | (df=='') | (df=='NaN'))
```

Now, we will replace '' and 'NaN' to null values


```{r}
df[df=='']<-NA
df[(df=='NaN')]<-NA

```



```{r}
colSums((is.na(df)) )

```


NULL TREATMENT

since  the null values of the attribute rating are higher than 10% of the sample. We cannot rid of these observations. So those values will be filled in.


let's check the rating distribution by plotting box plot.

```{r}
boxplot(df$Rating)
```
let check how many rows are greater than 5
```{r}
mode(df$Rating)


df$Rating[is.na(df$Rating)]<-4.4
```


```{r}
df[df$Rating>5,]
```
A outlier was found. as it is only one, it can be removed.

```{r}
df<- df[df$Rating<=5,]
length(df$Rating)
```
Now we have 10840 rows. Let check again the boxplot.

```{r}
boxplot(df$Rating)
```

As there are too many outliers, the mode was used for replacing the null values.




```{r}
colSums((is.na(df)) )
```
Once all null value of rating are replaced by the its mode, all others null values can be removed  due to are less than 1%.

let's check the rows with any of he values in null.

```{r}
df[!complete.cases(df),]
```
let rid of them
```{r}
df<-na.omit(df)
```


# quality data


Due to the price attribute format is incorrect, we should replace the dots(.) to 

```{r}
df$Price<-gsub('(\\$|,)','',df$Price)
```


```{r}
df$Category<- as.factor(df$Category)
df$Rating<- as.numeric(df$Rating)
df$Reviews<- as.numeric(df$Reviews)
df$Installs<- as.factor(df$Installs)

df$Price<- as.numeric(df$Price)
```

```{r}
colSums((is.na(df)) )
```









The reason why we replace 'Varies with device' value from the size column is because it represents more than 15% of whole dataframe and eliminating these values would represent a significant loss in data changing them on the other hand is a necessary step to convert the values for categorical to numeric. 

```{r}
df$Size
as.numeric(gsub('M','',df$Size)) 
```




```{r}
df$App<- as.character(df$App)
df$Category<- as.factor(df$Category)
df$Rating<- as.numeric(df$Rating)
df$Reviews<- as.numeric(df$Reviews)
```



Let's check the null values in the dataframe

```{r}
sum(is.na(df))
```


```{r}
sum(df=='')
```

```{r}
summary(df)
```


#### reviewing the data

```{r}

```

```{r}
df$Size_converted<- gsub('M','',df$Size)

"Varies with device"
```

```{r}
#df$Size_converted

```

```{r}
pairs(df[,]) ## correlation 

cor(df$Rating,df$Reviews)
```



```{r}
df$App<- as.character(df$App)
df$Category<- as.factor(df$Category)
df$Rating<- as.numeric(df$Rating)
df$Reviews<- as.numeric(df$Reviews)
df$Category<- as.factor(df$Category)
df$Category<- as.factor(df$Category)
df$Category<- as.factor(df$Category)
```

