---
title: "Project"
author: "Andres Viloria"
date: "2022-10-27"
output: pdf_document
---
#### Load the data
```{r}
df<-read.csv('googleplaystore.csv')
```

```{r}
colSums((is.na(df)) | (df=='') | (df=='NaN'))
```

Now, we will replace '' and 'NaN' to null values


```{r}
df[df=='',]
```



```{r}
df[df$Content.Rating=='',]
df[df$App=='',]
```

```{r}
df[df==""]<-NA
df[(df=='NaN')]<-NA
```


```{r}
colSums((is.na(df)) )
```

The reason why we replace 'Varies with device' value from the size column is because it represents more than 15% of whole dataframe and eliminating these values would represent a significant loss in data changing them on the other hand is a necessary step to convert the values for categorical to numeric. 

```{r}
df$Size
as.numeric(gsub('M','',df$Size)) 
```




```{r}
df$App<- as.character(df$App)
df$Category<- as.factor(df$Category)
df$Rating<- as.numeric(df$Rating)
df$Reviews<- as.numeric(df$Reviews)
```



Let's check the null values in the dataframe

```{r}
sum(is.na(df))
```


```{r}
sum(df=='')
```

```{r}
summary(df)
```


#### reviewing the data

```{r}

```

```{r}
df$Size_converted<- gsub('M','',df$Size)

"Varies with device"
```

```{r}
#df$Size_converted

```

```{r}
pairs(df[,]) ## correlation 

cor(df$Rating,df$Reviews)
```



```{r}
df$App<- as.character(df$App)
df$Category<- as.factor(df$Category)
df$Rating<- as.numeric(df$Rating)
df$Reviews<- as.numeric(df$Reviews)
df$Category<- as.factor(df$Category)
df$Category<- as.factor(df$Category)
df$Category<- as.factor(df$Category)
```

